Predicting information integration in pragmatic word learning across development

### 2021-01-05 papers/cogsci2019/cogsci2019.Rmd
prep for re-submission

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(matrixStats)
library(coda)
library(ggpubr)
library(lme4)
library(broom)
library(exactRankTests)
```

@@

pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(tidyverse)
library(knitr)
library(ggthemes)
library(langcog)
library(matrixStats)
library(coda)
library(ggpubr)
library(lme4)
library(broom.mixed)
library(exactRankTests)
```

@@

pred_ex3 <- readRDS(file = "saves/model_predictions_ex3_1.rds")%>%ungroup()

### 2021-01-05 papers/full_paper/Supplementary_information.Rmd
prep for re-submission

ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

ggplot(ex4_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

```{r child_prag_bf, results = "asis"}
child_ex3_model_comparison <- readRDS("../../stats/saves/child_ex3_model_comparison.rds")
child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
  filter(model == "pragmatic")%>%
  spread(parameter, logP) %>%
  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
         "noise > parameter free" = exp(noise - `parameter free`),
         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
  select(-model,-`parameter free`,-`developmental noise`, -noise)%>%
  gather(Comparison, BF)%>%
  mutate(BF = formatC(BF,2))
apa_table(
  child_ex3_pragmatic_models_bf
  , caption = "Model comparisons for integration models in Experiment 7"
  , note = "BF = Bayes Factor"
  , escape = T
)
```

@@

```{r child_bf, results = "asis", out.width="100%"}
child_ex3_bf <- child_ex3_model_comparison%>%
  rename(Parameter = parameter)%>%
  group_by(Parameter)%>%
  spread(model, logP) %>%
  mutate("Int > No CG" = formatC(exp(pragmatic - flat_prior),2),
         "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
         "No CG > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

@@

```{r}
child_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No common ground")
  )
child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))
```

@@

child_dev_noise_plot <- ggplot(developmental_noise_parameter, aes(x = age, y= y, col = Model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#b58900","#6c71c4","#859900"))
```

>>>>

ggplot(ex3_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

ggplot(ex4_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

```{r child_prag_bf, results = "asis"}
child_ex3_model_comparison <- readRDS("../../stats/saves/child_ex3_model_comparison.rds")
child_ex3_pragmatic_models_bf <- child_ex3_model_comparison%>%
  select(-ci_lower, -ci_upper)%>%
  filter(model == "pragmatic")%>%
  spread(parameter, logP) %>%
  mutate("dev. noise > noise" = exp(`developmental noise` - noise),
         "noise > parameter free" = exp(noise - `parameter free`),
         "dev. noise > parameter free" = exp(`developmental noise` - `parameter free`)) %>%
  select(-model,-`parameter free`,-`developmental noise`, -noise)%>%
  gather(Comparison, BF)%>%
  mutate(BF = formatC(BF,2))

apa_table(
  child_ex3_pragmatic_models_bf
  , caption = "Model comparisons for integration models in Experiment 7"
  , note = "BF = Bayes Factor"
  , escape = T
)
```

@@

```{r child_bf, results = "asis", out.width="100%"}
child_ex3_bf <- child_ex3_model_comparison%>%
  select(-ci_lower, -ci_upper)%>%
  rename(Parameter = parameter)%>%
  group_by(Parameter)%>%
  spread(model, logP) %>%
  mutate("Int > No CG" = formatC(exp(pragmatic - flat_prior),2),
         "Int > No Inf" = formatC(exp(pragmatic - prior_only),2),
         "No CG > No Inf" = formatC(exp(flat_prior - prior_only),2)) %>%
  select(-pragmatic,-flat_prior, -prior_only)

@@

```{r}
child_noise_parameters <- bind_rows(
  readRDS("../../stats/saves/child_ex3_pragm_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "Integration"),
  readRDS("../../stats/saves/child_ex3_prior_only_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No informativeness"),
  readRDS("../../stats/saves/child_ex3_flat_prior_model_noise.rds") %>%
  filter(Parameter %in% c("noise"))  %>%
  mutate(Model = "No common ground")
  )
child_noise_plot <- ggplot(child_noise_parameters, aes(x = value, col = Model, fill = Model))+
  geom_density(alpha = .5)+
  theme_few()+
  xlab("Noise parameter")+
  xlim(0,1)+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))+
  scale_fill_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```

@@

child_dev_noise_plot <- ggplot(developmental_noise_parameter, aes(x = age, y= y, col = Model))+
  geom_line(size = 1)+
  ylab("Noise parameter")+
  xlab("Age")+
  ylim(0,1)+
  theme_few()+
  scale_color_manual(breaks=c("Integration","No informativeness","No common ground"),
                    values= c("#C5D86D","#86615C","#AFE0CE"))
```
